---
output: rmarkdown::github_document
---

# publicwww

Query the 'PublicWWW' Source Code Search Engine

## Description

The 'PublicWWW' <https://publicwww.com/> source code search engine indexes the content 
of over 200 million web sites and provides a query interface that lets the
caller find any alphanumeric snippet, signature or keyword in the web pages 
'HTML', 'JavaScript' and 'CSS' style sheet code. 

## NOTE

The site requires an [API key](https://publicwww.com/pricing.html) and has limited
functionality under the free plan.

## What's Inside The Tin

The following functions are implemented:

- `source_code_search`:	Find any alphanumeric snippet, signature or keyword in the web pages HTML, JS and CSS code in the PublicWWW database

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/publicwww")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(publicwww)
library(tidyverse)

# current verison
packageVersion("publicwww")

```

### Sites using the WordPress theme "Twenty Sixteen":

```{r cache=TRUE}
source_code_search('"/wp-content/themes/twentysixteen/"')
```

### Sites running the coinhive JS miner

```{r cache=TRUE}
source_code_search('"coin-hive.com/lib/coinhive.min.js"')
```

### Sites (theoretically) running Drupal

```{r cache=TRUE}
source_code_search('"/sites/all/themes/"', snippets = TRUE)
```
